---
title: "Elections France 2017 Data Merge"
output:  github_document
---
```{r}
library(plyr)
library(dplyr)

library(tidyr)
library(stringr)
library(GGally)
library(ggcorrplot)
library(lsr)
```



```{r}
df_communes<- read.csv('data/DOI/OGR_Communes.csv',colClasses=c(INSEE_COM='character',CODE_COM='character',CODE_DEPT='character',CODE_ARR='character')) %>% select(CODE_COM,INSEE_COM,NOM_COM,CODE_ARR,CODE_DEPT,NOM_DEPT,CODE_REG,NOM_REG,POPULATION)
df_communes<-df_communes %>%  unite(CODGEO_ARR_NO,CODE_DEPT,CODE_ARR,sep='',remove=FALSE)
df_communes<-df_communes %>%  mutate(CODE_COM=str_pad(CODE_COM, 3, pad = "0"))
df_communes<-df_communes %>%  mutate(CODE_ARR=str_pad(CODE_ARR, 3, pad = "0"))
df_communes<-df_communes %>%  unite(CODGEO_ARR,CODE_DEPT,CODE_ARR,sep = '')

str(df_communes)

```
### Combine with 2012 First round votes  for LEPEN(FN) HOLLANDE(PS) SARKOZY(LR):
```{r}
df.votes.2012<-read.csv('data/DOI/presidentielle_2012_T1_communes.csv')
df.votes.2012<-df.votes.2012 %>%  mutate(CodeInsee=str_pad(CodeInsee, 5, pad = "0"))
df.votes.2012$CodeInsee<-as.character(df.votes.2012$CodeInsee)
df.votes.2012 <- df.votes.2012 %>% mutate(LE.PEN_2012=LePen/Exprimés)
df.votes.2012 <- df.votes.2012 %>% mutate(HOLLANDE_2012=Hollande/Exprimés)
df.votes.2012 <- df.votes.2012 %>% mutate(SARKOZY_2012=Sarkozy/Exprimés)
df.votes.2012 <- df.votes.2012 %>% mutate(MELENCHON_2012=Mélenchon/Exprimés)

df.votes.2012 <- df.votes.2012 %>% select(CodeInsee,LE.PEN_2012,HOLLANDE_2012,SARKOZY_2012,MELENCHON_2012)

df.all<-left_join(df_communes,df.votes.2012,by=c('INSEE_COM'='CodeInsee'))
str(df.all)
```
### Combine with 2017 second round :

```{r}
df_votes.2017_2ndRound<-read.csv('data/DOI/Presidentielle_2017_Resultats_Communes_Tour_2.csv',stringsAsFactors = F)


df_votes.2017_2ndRound<-df_votes.2017_2ndRound %>%  mutate(CODE_COM=str_pad(Code.de.la.commune, 3, pad = "0"))
df_votes.2017_2ndRound<-df_votes.2017_2ndRound %>%  mutate(CODE_DEPT=str_pad(Code.du.département, 2, pad = "0"))
df_votes.2017_2ndRound<-df_votes.2017_2ndRound %>%  unite(GEOCODE_COM,CODE_DEPT,CODE_COM,sep = '')
df_votes.2017_2ndRound<- df_votes.2017_2ndRound %>% select(-Code.de.la.commune,-Libellé.de.la.commune,-Code.du.département,-Libellé.du.département)

df.all_2<-merge(df.all,df_votes.2017_2ndRound,by.x='INSEE_COM',by.y='GEOCODE_COM',all.x=TRUE)

View(df.all_2 %>% filter(CODE_REG=='53' | CODE_COM==41269) %>% arrange(desc(X..Voix.Exp.1)) %>% select(NOM_COM,NOM_DEPT,X..Voix.Exp, X..Voix.Exp.1))
```


### Combine with 2017 First round votes :

```{r}
candidats<-c("ARTHAUD","ASSELINEAU","CHEMINADE","DUPONT.AIGNAN","FILLON","HAMON","LASSALLE","LE.PEN","MACRON","MÉLENCHON","POUTOU")

df_votes.2017<-read.csv('data/DOI/pres_1erTour_2017_commune_candidat.csv',stringsAsFactors = F)
df_votes.2017<-df_votes.2017 %>%  mutate(CODE_COM=str_pad(Code.de.la.commune, 3, pad = "0"))
df_votes.2017<-df_votes.2017 %>%  mutate(CODE_DEPT=str_pad(Code.du.département, 2, pad = "0"))
df_votes.2017<-df_votes.2017 %>%  unite(GEOCODE_COM,CODE_DEPT,CODE_COM,sep = '')
df_votes.2017<- df_votes.2017 %>% select(-Code.de.la.commune,-Libellé.de.la.commune,-Code.du.département,-Libellé.du.département)
df_votes.2017 <- df_votes.2017 %>% mutate_at(candidats,funs(./100))
df.all<-merge(df.all,df_votes.2017,by.x='INSEE_COM',by.y='GEOCODE_COM',all.x=TRUE)

df.all %>% filter(INSEE_COM=='32009')
```




```{r}
str(df_votes.2017_2ndRound)
```

### Compute vote evolution for the four main parties :

```{r}
df.all<-df.all %>% mutate(EVOLUTION_FN=LE.PEN-LE.PEN_2012)
df.all<-df.all %>% mutate(EVOLUTION_PS=HAMON-HOLLANDE_2012)
df.all<-df.all %>% mutate(EVOLUTION_LR=FILLON-SARKOZY_2012)
df.all<-df.all %>% mutate(EVOLUTION_FDG=MÉLENCHON-MELENCHON_2012)
```


### Combine with Population and add Unemployment rate

```{r}

df.emploi.COM<-read.csv('data/DOI/base_cc_emploi_pop_active_13_COM.csv',stringsAsFactors = F, colClasses=c(CODGEO='character'))
df.emploi.COM<- df.emploi.COM %>% mutate(CODGEO=str_pad(CODGEO, 5, pad = "0"))

add_employment_stats <- function(df){
 df<- df %>% select(CODGEO,P13_ACT1564,P13_ACT1524,P13_ACT2554,P13_ACT5564,P13_CHOM1564
,P13_HCHOM1564,P13_HCHOM1524,P13_HCHOM2554,P13_HCHOM5564,P13_FCHOM1564,P13_FCHOM1524,P13_FCHOM2554,P13_FCHOM5564,C13_ACT1564_CS1,C13_ACT1564_CS2,C13_ACT1564_CS3,C13_ACT1564_CS4,C13_ACT1564_CS5,C13_ACT1564_CS6,P13_ETUD1564,P13_RETR1564)

df <- df %>% mutate(NoJob_all_ratio=P13_CHOM1564/P13_ACT1564)
df <- df %>%mutate(NoJob_1524_ratio=(P13_HCHOM1524+P13_FCHOM1524)/P13_ACT1524)
df <- df %>%mutate(NoJob_2554_ratio=(P13_HCHOM2554+P13_FCHOM2554)/P13_ACT2554)
df <- df %>%mutate(NoJob_5564_ratio=(P13_HCHOM5564+P13_FCHOM5564)/P13_ACT5564)
df <- df %>% mutate(Job_AGRO_ratio=C13_ACT1564_CS1/P13_ACT1564)
df <- df %>% mutate(Job_ARTISAN_ratio=C13_ACT1564_CS2/P13_ACT1564)
df <- df %>% mutate(Job_CADRE_ratio=C13_ACT1564_CS3/P13_ACT1564)
df <- df %>% mutate(Job_INTERMED_ratio=C13_ACT1564_CS4/P13_ACT1564)
df <- df %>% mutate(Job_EMPLOYE_ratio=C13_ACT1564_CS5/P13_ACT1564)
df <- df %>% mutate(Job_OUVRIER_ratio=C13_ACT1564_CS6/P13_ACT1564)
df <- df %>% mutate(Etudiants_ratio=P13_ETUD1564/P13_ACT1564)
df <- df %>% mutate(Retraites_ratio=P13_RETR1564/P13_ACT1564) 

df<-df %>% select(-matches('P13|C13'))


return(df)
}

df.emploi.COM<-add_employment_stats(df.emploi.COM)
df.all<-merge(df.all,df.emploi.COM,by.x='INSEE_COM',by.y='CODGEO',suffixes=c('','_COM'),all.x=TRUE)


# compute value per ARR
#df.all <- df.all %>% group_by(CODGEO_ARR) %>% mutate_at(vars(matches('Job')),funs(total=sum(.,na.rm=TRUE)))

df.all %>% filter(grepl('ROSTR',NOM_COM))
df.all %>% filter(grepl('SAINT-NICOLAS-DU-PELEM',NOM_COM)) %>% gather()


```

# Add Incomes indicators
## per town

```{r}
df.income.COM<-read.csv('data/DOI/FILO_DEC_COM.csv') %>% select(CODGEO,Q213,Q3_Q1,RD,GI13)
str(df.income.COM)
df.all<-merge(df.all,df.income.COM,by,by.x='INSEE_COM',by.y='CODGEO',all.x=TRUE)
sum(is.na(df.all$Q213))
dim(df.all)
```

## per County and replace missing town incomes by county incomes.
```{r}
df.income.ARR<-read.csv('data/DOI/FILO_DEC_ARR.csv') %>% select(CODGEO,Q213,Q3_Q1,RD,GI13)

df.all<- merge(df.all,df.income.ARR,by.x="CODGEO_ARR_NO",by.y='CODGEO',all.x=TRUE,suffixes=c('','_ARR'))

df.all <- df.all %>% mutate(Q213.Data.Available= ifelse(is.na(Q213),FALSE,TRUE))
df.all <- df.all %>% mutate(Q3_Q1.Data.Available= ifelse(is.na(Q3_Q1),FALSE,TRUE))

df.all<-df.all %>% mutate(Q213=ifelse(is.na(Q213),Q213_ARR,Q213))
df.all<-df.all %>% mutate(Q3_Q1=ifelse(is.na(Q3_Q1),Q3_Q1_ARR,Q3_Q1))
sum(is.na(df.all$Q213))
```

# Add foreigners

```{r}

# add ratio of foreigners
df.foreigners<-read.csv('data/DOI/BTX_TD_NAT1_2013.csv')
colnames(df.foreigners)
df.foreigners%>%  select(contains('INATC'))
df.foreigners <- df.foreigners %>% mutate(total_pop= df.foreigners %>%rowwise() %>% select(contains('INATC')) %>% rowSums())
df.foreigners <- df.foreigners %>% mutate(total_foreigners= df.foreigners %>%rowwise() %>% select(contains('INATC2')) %>% rowSums())
df.foreigners <- df.foreigners %>% mutate(ratio_foreigners= total_foreigners/total_pop)
df.foreigners %>% filter(CODGEO=='01001') %>% gather()
df.foreigners <- df.foreigners %>% select(CODGEO,ratio_foreigners)

df.all<-merge(df.all,df.foreigners,by.x='INSEE_COM',by.y='CODGEO')

df.all %>% filter(grepl('PARIS',NOM_COM)) %>% select(ratio_foreigners)

```

## Add migrations

```{r}

df.immigrants<-read.csv('data/DOI/BTX_TD_IMG1A_2013.csv')
colnames(df.foreigners)
df.immigrants%>%  select(contains('INATC'))
df.immigrants <- df.immigrants %>% mutate(total_pop= df.immigrants %>%rowwise() %>% select(contains('IMMI')) %>% rowSums())
df.immigrants <- df.immigrants %>% mutate(total_immigrants= df.immigrants %>%rowwise() %>% select(contains('IMMI1')) %>% rowSums())
df.immigrants <- df.immigrants %>% mutate(ratio_immigrants= total_immigrants/total_pop)
df.immigrants %>% filter(CODGEO=='01001') %>% gather()
df.immigrants <- df.immigrants %>% select(CODGEO,ratio_immigrants)

df.all<-merge(df.all,df.immigrants,by.x='INSEE_COM',by.y='CODGEO')

df.all %>% filter(grepl('VENDOME',NOM_COM)) %>% select(contains('ratio'))

```
## Add immigrants job ratio

```{r}
df.immigrants_job<-read.csv('data/DOI/BTX_TD_IMG3A_2013.csv')


df.immigrants_job <- df.immigrants_job %>% mutate(total_AGRO= df.immigrants_job %>%rowwise() %>% select(contains('CS1_81')) %>% rowSums())
df.immigrants_job <- df.immigrants_job %>% mutate(total_ARTISANS= df.immigrants_job %>%rowwise() %>% select(contains('CS1_82')) %>% rowSums())
df.immigrants_job <- df.immigrants_job %>% mutate(total_CADRE= df.immigrants_job %>%rowwise() %>% select(contains('CS1_83')) %>% rowSums())
df.immigrants_job <- df.immigrants_job %>% mutate(total_INTER= df.immigrants_job %>%rowwise() %>% select(contains('CS1_84')) %>% rowSums())
df.immigrants_job <- df.immigrants_job %>% mutate(total_EMPLOYE= df.immigrants_job %>%rowwise() %>% select(contains('CS1_85')) %>% rowSums())

df.immigrants_job <- df.immigrants_job %>% mutate(total_OUVRIER= df.immigrants_job %>%rowwise() %>% select(contains('CS1_86')) %>% rowSums())

df.immigrants_job <- df.immigrants_job %>% mutate(total_RETRAITE= df.immigrants_job %>%rowwise() %>% select(contains('CS1_87')) %>% rowSums())


df.immigrants_job <- df.immigrants_job %>% mutate(ratio_immigrants_AGRO= (CS1_81_IMMI1_SEXE1+CS1_81_IMMI1_SEXE2)/total_AGRO)
df.immigrants_job <- df.immigrants_job %>% mutate(ratio_immigrants_ARTISANS= (CS1_82_IMMI1_SEXE1+CS1_82_IMMI1_SEXE2)/total_ARTISANS)
df.immigrants_job <- df.immigrants_job %>% mutate(ratio_immigrants_CADRE= (CS1_83_IMMI1_SEXE1+CS1_83_IMMI1_SEXE2)/total_CADRE)
df.immigrants_job <- df.immigrants_job %>% mutate(ratio_immigrants_INTER= (CS1_84_IMMI1_SEXE1+CS1_84_IMMI1_SEXE2)/total_INTER)
df.immigrants_job <- df.immigrants_job %>% mutate(ratio_immigrants_EMPLOYE= (CS1_85_IMMI1_SEXE1+CS1_85_IMMI1_SEXE2)/total_EMPLOYE)
df.immigrants_job <- df.immigrants_job %>% mutate(ratio_immigrants_OUVRIER= (CS1_86_IMMI1_SEXE1+CS1_86_IMMI1_SEXE2)/total_OUVRIER)
df.immigrants_job <- df.immigrants_job %>% mutate(ratio_immigrants_RETRAITE= (CS1_87_IMMI1_SEXE1+CS1_87_IMMI1_SEXE2)/total_RETRAITE)

                                                    

df.immigrants_job <- df.immigrants_job %>% select(CODGEO,contains('ratio'))

df.all<-merge(df.all,df.immigrants_job,by.x='INSEE_COM',by.y='CODGEO')

df.all %>% filter(grepl('VILLEBAROU',NOM_COM)) %>% select(contains('ratio'))

```
## Add education level

```{r}
df.education<-read.csv('data/DOI/base-cc-diplomes-formation-2013_v2.csv')
df.education$CODGEO<-as.character(df.education$CODGEO)
df.education<-df.education %>% mutate(education_no_diplom_ratio=P13_NSCOL15P_DIPLMIN/P13_NSCOL15P)
df.education<-df.education %>% mutate(education_CAPBEP_ratio=P13_NSCOL15P_CAPBEP/P13_NSCOL15P)
df.education<-df.education %>% mutate(education_BAC_ratio=P13_NSCOL15P_BAC/P13_NSCOL15P)
df.education<-df.education %>% mutate(education_SUP_ratio=P13_NSCOL15P_SUP/P13_NSCOL15P)
df.education %>% filter(CODGEO=="01001") %>% gather()
df.all<- left_join(df.all,df.education %>% select(CODGEO,education_no_diplom_ratio,education_CAPBEP_ratio,education_BAC_ratio,education_SUP_ratio),by=c('INSEE_COM'='CODGEO'))
```
## Add family status

```{r}
df.family<-read.csv('data/DOI/BTX_TD_FAM1_2013.csv')
df.family$CODGEO<-as.character(df.family$CODGEO)
df.family$family_monoparental<-df.family %>% select(matches('TF1211|TF1212|TF1221|TF1222')) %>% rowSums(.)
df.family$total= df.family %>% select(contains('NBENF')) %>% rowSums(.)
df.family$family_monoparental_ratio<- df.family$family_monoparental/df.family$total
df.all<- left_join(df.all,df.family %>% select(CODGEO,family_monoparental_ratio),by=c('INSEE_COM'='CODGEO'))

```

# Add miscellaneous features (such as number of Shop, Camping, Hotels)
```{r}

df_misc.param<-read.csv('data/DOI/MDB-INSEE-V2.csv',stringsAsFactors = F)
df.all<-merge(df.all,df_misc.param,by.x='INSEE_COM',by.y='CODGEO',all.x=TRUE)

```



Focus on one city :
```{r}
df.all %>% filter(INSEE_COM==22007) %>% gather()
```
### Convert Indicators based on absolute values ('Nb.') into logarithmic ratio :
```{r}
df.all<-df.all %>% mutate_each(funs(ratio=log(./Population+1)),contains('Nb.'))
```

## Add best candidate per town:
```{r}
df.all2<-df.all %>% select(one_of(candidats)) %>% mutate(best_candidate= names(.)[max.col(.)]) 
table(df.all2$best_candidate)
df.all$best_candidate <- df.all2$best_candidate
  
```

## Replace N/A on ratio with Zeros and infinite with 1:
```{r}
ratio_features<- grep('ratio',colnames(df.all),value = TRUE)

df.all <- df.all %>% mutate_at(ratio_features,funs(ifelse(is.na(.),0,.)))
df.all <- df.all %>% mutate_at(ratio_features,funs(ifelse(is.infinite(.),1,.)))
```

## Add Population category

```{r}

df.all$Population_cat<- cut(df.all$POPULATION, breaks=c(0, 100, 300,500,1000,2000,5000,1000000),include.lowest = TRUE )
df.all$Population_cat<-revalue(df.all$Population_cat, c("[0,100]"="<100","(100,300]"="[100,300]","(300,500]"="[300,500]", "(500,1e+03]"="[500,1000]","(1e+03,2e+03]"="[1000,2000]", "(2e+03,5e+03]"="[2000,5000]","(5e+03,1e+06]"=">10000"))

```


## Save final dataframe
```{r}
df.all[is.na(df.all$HOLLANDE_2012),]
write.csv(df.all,'data/DOI/elections_2017_First_round.csv')
```
